Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-03 pkg/disttree/inst/draft/rejoinder.tex
further revisions, also adapted to changes in the manuscript and the supplements
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2307 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 75ba5d90d4c34e226ab5d13fdb064c2e4136d22e

It is difficult to set a minimal size of the learning data for
the method to be effective, however, the distributional forest
performed quite well in different applications with at least
50 observations. 
The stopping criteria that are based on the number of 
observations in a node need to be adapted to the size of the
learning data, especially if the data set is small.
For example, in the application presented in this paper the 
learning data consists of 744 observations and each tree is built
on a subsample of around 470 observations (63.2 percent, as 
this is the mean fraction for N-out-of-N bootstrapping with 
replacement and therefore commonly used for subsampling
in forest models). 
The stopping criteria are set such that no split will be performed 
if there are either less than 50 observations 
in the considered node or if there were less than 20 observations in 
one of the resulting subgroups of the considered possible split.
(This information is now also added in Section~3.2., 'Distributional forest').
Generally, these values (and also the significance level for
the statistical tests in the tree algorithm) should be kept 
rather low for a forest model as it is desirable to grow very 
large trees. Therefore, each of the trees in the forest will 
most likely overfit the subsample it is learned on, however, this 
is evened out by combining them to a forest model (with an adequate 
number of trees). For that reason, setting the stopping criteria too 
low does not lead to a decrease in goodness of fit, however, the 
computational costs might increase, especially for large data sets. 
On the other hand, if they are too high, splits might not be detected 
such that the corresponding effects are not captured by the model.

@@

With `domain knowledge' we are referring to expert knowledge 
in the field of the considered application. 
If variable selection and further model specifications have 
to be made in advance this additional knowledge is required 
in order to make reasonable decisions.

\begin{reto}
Im paper entsprechend adressieren (tbd).
\end{reto}

@@

These are the residuals of precipitation on the transformed scale.

@@

You are right, the observations can not be negative and are 
therefore left-truncated at 0 and not left-censored (we have adapted 
this in the caption of Figure~3). However, due to days without 
rain there is a naturally given point mass at zero in precipitation 
data, similar to the point mass that results from censoring 
possibly negative data.
Thus, we use the concept of \textit{censoring} which allows us to directly
account for the large fraction of observations at zero and the non-negative
part of the observations at once.
The online supplement which comes along with our manuscript includes the
results for a hurdle model where the occurrence of precipitation is addressed
using a binary model while the non-negative part is
modeled by a \textit{truncated} Gaussian distribution.

@@

Since we are applying a censored distribution as explained above we 
prefer using the term censoring point, even though the data itself 
is not censored.

@@

See points 3 and 4.

@@

\textit{FIX ME: ?}

@@

\begin{reto}
Beide? Verstehe ich den Kollegen da richtig?
\end{reto}

@@

% load("~/svn/partykit/pkg/disttree/inst/draft/Axams_24to4.rda")
% sgb <- stabsel(gb, cutoff = 0.6, q = 30)

@@

>>>>

The required size of the training data depends heavily on the complexity 
of the model, however, in different applications which we have tested the 
distributional forest on it performed quite well with at least 50 observations. 
Generally, the stopping criteria \texttt{minbucket} and \texttt{minsplit} (both 
determining the minimal number of observations in a node) and \texttt{alpha} 
(the significance level for the statistical tests in the tree algorithm) should 
be kept rather low for a forest model as it is desirable to grow very large trees. 
(FIX ME: reference?)
Therefore, each of the trees in the forest will most likely overfit the subsample 
it is learned on, however, this is evened out by combining them to a forest 
model (with an adequate number of trees). (FIX ME: reference?) 
For that reason, setting the stopping criteria too low does not lead to a decrease 
in goodness of fit, however, the computational costs might increase, especially for 
large data sets. On the other hand, if they are too high, splits might not be detected 
such that the corresponding effects are not captured by the model.

@@

We have rephrased this as 'expert knowledge in the application domain'
in Section~2.2..

@@

The residual QQ plots (Dunn et al. 1996) illustrate the probability 
integral transform (PIT, Gneiting et al. 2007) values of the observations 
in the testing data and are therefore scale invariant. A more detailed 
explanation can be found in Supplement 2 (Stationwise Evaluation).

@@

You are right, our explanation was incorrect, thank you for pointing
this out! We have now clarified that the model employs a censored
distribution but the observations are not censored, just non-negative
with a point mass at 0.

@@

We have rephrased this part of the caption to 'Observations are non-negative 
and modeled by a Gaussian distribution, left-censored at 0.
The observations are depicted by crosses and the predicted point mass
from the model by filled circles.' to clearly distinguish between the model
and the observations.

@@

See point 4.

@@

We have rephrased this to 'For each distributional tree a different learning 
data set is obtained ... '

@@

The PIT histograms and the residual QQ plots visualize the same
results on different scales. The out-of-sample PIT values are 
either plotted in a histogram or plotted against the corresponding
quantiles of the standard normal distribution. A more detailed 
explanation can be found in Supplement 2 (Stationwise Evaluation) 
which contains both, PIT histograms and residual QQ plots, 
for 15 stations. In the manuscript we decided to show only the 
residual QQ plot as it allows for a better analysis of tail 
behaviour than the PIT histogram.

@@

% load("~/svn/partykit/pkg/disttree/inst/draft/Axams_24to4.rda")
% gb <- Axams_24to4$gb
% sgb <- stabsel(gb, cutoff = 0.6, q = 30)

@@

\item[] Dunn, P. K. and Smyth, G. K. (1996).
Randomized Quantile Residuals,
\textit{Journal of Computational and Graphical Statistics}
\textbf{5, 3}: 236--244.

\item[] Gneiting, T., Balabdaoui, F. and Raftery, A. E. (2007).
Probabilistic Forecasts, Calibration and Sharpness,
\textit{Journal of the Royal Statistical Society B}
\textbf{69, 2}: 243--268.
